### 2014-04-02 Docs/architecture/architecture.tex
more runtime parameters

The global index space covers the entire domain at a given resolution.
For a simulation setup with \runparam{n\_cellx = 32} and \runparam{n\_celly =
  32}, the coarsest level (level 1) has $32 \times 32$ zones, and the
global index space will run from $0, \ldots, 31$ in each coordinate
direction.  Level 2 will have a global index space running from $0,
\ldots, 63$ in each coordinate direction (corresponding to $64 \times
64$ zones if fully refined), and level 3 will have a global index
space running from $0, \ldots, 127$ in each coordinate direction
(corresponding to $128\times 128$ zones if fully refined).

>>>>

The global index space covers the entire domain at a given resolution.
For a simulation setup with \runparam{n\_cellx} {\tt = 32} and \runparam{n\_celly} {\tt =
  32}, the coarsest level (level 1) has $32 \times 32$ zones, and the
global index space will run from $0, \ldots, 31$ in each coordinate
direction.  Level 2 will have a global index space running from $0,
\ldots, 63$ in each coordinate direction (corresponding to $64 \times
64$ zones if fully refined), and level 3 will have a global index
space running from $0, \ldots, 127$ in each coordinate direction
(corresponding to $128\times 128$ zones if fully refined).
